Efficiently stable presentations from error-correcting codes

### 2023-06-30 efficient_stability.tex
few more comments

@@

For $q=2^t$ and $a\in \F_q$ we let $\kappa(a)\in\F_2^t$ denote the binary representation of $a$, taken in a fixed but usually left implicit self-dual basis of $\F_{q}$ over $\F_2$. We extend $\kappa$ to vectors over $\F_q$ coordinate-wise. We let $\tr(\cdot):\F_q\to\F_2$ denote the trace over $\F_2$. Because we chose a self-dual basis for the binary representation, the trace satisfies $\tr(ab)=\kappa(a)\cdot\kappa(b)$ \hnote{added:} where the right-hand side means the $\F_2$-inner product of the vectors $\kappa(a), \kappa(b)$.

Let $q=2^t$ and $\code$ an $[n,k,d]_q$ linear code. Let $\code_{\Had}$ be the Hadamard code over $\F_2^t$ (introduced at the end of Section~\ref{sec:pres-code}). Let $T=2^t$.
Let $\code'$ be the $[Tn,tk,d']$ linear code over $\F_2$ defined as follows. Given $a\in (\F_2^t)^{k}$, first map $a\mapsto a'=\kappa^{-1}(a) \in \F_q^{k}$. Then encode $a'$ to $b'=\code_\RM(a')\in \F_q^n$. Finally, return $b=\code_\Had(\kappa(b'))\in(\F_2^T)^n$, where $\code_\Had$ is applied component-wise. Using that $\code_\Had$ has relative distance $\frac{1}{2}$, it is easy to verify that this code has distance $d'\geq dT/2$.

@@

>>>>

\hnote{There shoudl be some lemma or theorem statement saying that this is in fact a tester, right? Perhaps cite BFL?}

@@

For $q=2^t$ and $a\in \F_q$ we let $\kappa(a)\in\F_2^t$ denote the binary representation of $a$, taken in a fixed but usually left implicit self-dual basis of $\F_{q}$ over $\F_2$. We extend $\kappa$ to vectors over $\F_q$ coordinate-wise. We let $\tr(\cdot):\F_q\to\F_2$ denote the trace over $\F_2$. Because we chose a self-dual basis for the binary representation, the trace satisfies $\tr(ab)=\kappa(a)\cdot\kappa(b)$ \hnote{added:} where the right-hand side means the $\F_2$-inner product of the vectors $\kappa(a), \kappa(b)$. \hnote{added:} For more details on the $\kappa$ map and its properties, see~\cite[Section 3.3]{ji2020mip}.

Let $q=2^t$ and $\code$ an $[n,k,d]_q$ linear code. Let $\code_{\Had}$ be the Hadamard code over $\F_2^t$ (introduced at the end of Section~\ref{sec:pres-code}). Let $T=2^t$.
Let $\code'$ be the $[Tn,tk,d']$ linear code over $\F_2$ defined as follows. Given $a\in (\F_2^t)^{k}$, first map $a\mapsto a'=\kappa^{-1}(a) \in \F_q^{k}$. Then encode $a'$ to $b'=\code_\RM(a')\in \F_q^n$ \hnote{should this be $\code$ or $\code_\RM$?}. Finally, return $b=\code_\Had(\kappa(b'))\in(\F_2^T)^n$, where $\code_\Had$ is applied component-wise. Using that $\code_\Had$ has distance $T/2$, it is easy to verify that this code has distance $d'\geq dT/2$.

@@

\hnote{I'm a little confused by the description of this local tester... This seems to just make $r$ queries, right (but it says $rq$ above)? And it feels like to ``simulate'' the check from $\code$, one has to make $2q$ random queries to the Hadamard code to decode the symbol from $\F_q$, right?}

\hnote{Also, probably could use another lemma or proposition here arguing that this is in fact a valid tester.}
